### 2023-03-12 main/chapter_2ljets.tex
explain (un)blinding

>>>>

Prediction is essential to the act of data analysis, because if a model
incorrectly predicts observations, then it follows logically that that model is
wrong.
Blinding hides the data until predictions are made, and is a powerful way to
ensure predictiveness.
A model that must see an observation before pretending to predict it is not
predicting the observation --- such a model is not blind.
Similarly, a model that cannot see an observation is blind and can at best
attempt predict it.
In our context, a blind analysis must fully determine all predictions in signal
regions before knowing what data lie in those signal regions.
We can remain blind while using other data, such as those in validation
regions, if those regions are unaffected by the signals, but to prematurely
peek into the signal regions would break the blinding and threaten to break our
models' predictiveness.

Unblinding is the act of looking at previously blinded data, and should be
undertaken only after our predictions are finalized.
